---
title: "This is my work in R"
abstract: 

output:
  bookdown::html_document2

bibliography: ZoteroExample.bib
csl: apa.csl

---

MyFirstName MyLastName

ThisIs mySchoolProgramName

ThisIs UniversityName

City, ZipCope, Country

username@the.rest

date: August 23, 2022

------------------------------------------------------------------------

Abstract

This is an example of an abstract in a paper. This is an example of an abstract in a paper.This is an example of an abstract in a paper. This is an example of an abstract in a paper.This is an example of an abstract in a paper.This is an example of an abstract in a paper.This is an example of an abstract in a paper.

------------------------------------------------------------------------

```{r, echo=FALSE}
knitr::knit_hooks$set(crop = knitr::hook_pdfcrop)
```


# Introduction

This is just my intro to my nice paper, I will explain the cool things I can do with my new skills combined with some Latex. This is just my intro to my nice paper, I will explain the cool things I can do with my new skills combined with some Latex. This is just my intro to my nice paper, I will explain the cool things I can do with my new skills combined with some Latex. This is just my intro to my nice paper, I will explain the cool things I can do with my new skills combined with some Latex.

This is just my intro to my nice paper, I will explain the cool things I can do with my new skills combined with some Latex.

# Exploring Data

Sections may use a label ^[This is a footnote.] In fact, you can have a label wherever you think a future reference to that content might be needed. This label is needed for referencing. For example the next subsection has label **categs**, so you can reference it by writing: As we see in section \@ref(categs).

```{r collecting, echo=FALSE}
# collecting
fileLink=url("https://github.com/profemagallanes-unmsm/FGV2022_rio/raw/main/DataFiles/mergedData.RDS")
mergedData=readRDS(fileLink)
```

## Exploring Categorical Data{#categs}

Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.

I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.

You can see the statistics of categorical variables in Table \@ref(tab:cat-exploreTable).

```{r cat-exploreTable,results='asis', warning=FALSE}
library(summarytools)
library(tidyr)
library(knitr)
library(kableExtra)

freq(mergedData[, 9], 
     plain.ascii = FALSE,
     report.nas=FALSE)%>%tb() %>%
  kable(format = "html", digits = 2,caption = "This is a table",col.names = c("Democracy Index","count","pct","pct_cumm"))%>%
  kable_styling(full_width = F)

```

You can see this variable plotted in Figure \@ref(fig:cat-Barplot).

```{r cat-Barplot, echo=FALSE, fig.cap="Freedom of Press in the world"}
tablePFI=as.data.frame(table(mergedData$PressFreedomIndex_or))
names(tablePFI)=c("var","count")

##
library(ggplot2)
base=ggplot(data=tablePFI,aes(x=var,y=count))
bar1=base + geom_bar(stat = 'identity')
bar1=bar1+labs(x="Press Freedom")

bar1
```

## Exploring Numerical Data

Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.

Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.

```{r summary-Numeric, results='asis', echo=FALSE, message=FALSE}

library(vtable)
st(mergedData[,c("DemocracyIndex","mili_pctGDP")])
```

In the Table \@ref(tab:summary-Numeric), you realize that the mean of military expenditure is **{**\bf\Sexpr{mean(mergedData$mili_pctGDP)}}.

It would be good to see a boxplot, check Figure \@ref(fig:num-Boxplot) below.

```{r num-Boxplot, echo=FALSE}
base=ggplot(data=mergedData)
box = base + geom_boxplot(aes(y=mili_pctGDP)) 
box = box + labs(x="", y = "% of country GDP")
box=box + theme(axis.text.x = element_blank(),
                axis.ticks.x = element_blank())

box
```

Boxplots were introduced by Tuckey @tukey_exploratory_1977. Compare [@tukey_exploratory_1977] or [-@tukey_exploratory_1977]

# Other plot

## A map{#map}

Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.

Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.

Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map.Let me show a nice map in Figure \@ref(fig:map-Plot).

```{r map-Plot, echo=FALSE, fig.cap="Calls to 911",message=FALSE}
library(ggplot2)
library(sf)
fileMapPoints="https://github.com/profemagallanes-unmsm/FGV2022_rio/raw/main/DataFiles/calls911_geo.geojson"
fileMapPolygons="https://github.com/profemagallanes-unmsm/FGV2022_rio/raw/main/DataFiles/MapSeattle.geojson"
events=read_sf(fileMapPoints)
city=read_sf(fileMapPolygons)


base=ggplot(city) + geom_sf() + theme_light()
eventsByTime=base + geom_sf(data = events,
                         size=0.5,
                         aes(color=nightTime)) 
eventsByTime
```

Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it.

## A word cloud{#wordPlot}

Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud. Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.Let me show a nice word cloud.

```{r dataForCloud, echo=FALSE}
location="https://github.com/profemagallanes-unmsm/FGV2022_rio/raw/main/DataFiles/rebelData.csv"
wordData=read.csv(location)

library(tidyr)

wordDataNames=separate_rows(wordData,StateName)
stateCounts=as.data.frame(table(wordDataNames$StateName))
names(stateCounts)=c("state","aCount")
```

```{r theCloud-plot, echo=FALSE, fig.cap="States and rebel movements",crop=TRUE}
library(ggwordcloud)

set.seed(123)
base = ggplot(stateCounts, aes(label = state,
                               size= aCount,
                               color = aCount))
cloudRebel= base + geom_text_wordcloud() + theme_minimal()

cloudRebel= cloudRebel+scale_color_gradient(low = "orange",
                                            high = "red") 

cloudRebel
```

Above you see our Figure \@ref(fig:theCloud-plot) Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.

It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it.

It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it. It has been a very hard work.Here, I continue doing this nice work, I hope you like it and read it.

# My Regression

Several times we need regression.

```{r regres, echo=FALSE}
h1=formula(mili_pctGDP~DemocracyIndex)
regre1=lm(h1,data=mergedData)

h2=formula(mili_pctGDP~DemocracyIndex + IndexofEconomicFreedom)
regre2=lm(h2,data=mergedData)
```

These is a nice summary for two regressions, as shown in Table \@ref(tab:regs1):

```{r regs1, echo=FALSE}

library(modelsummary)

models=list(regre1,regre2)
modelsummary(models, title = "Models for Military Expenditure",
             stars = TRUE,
             output = "kableExtra")
```

You can also do this: You can also do this:You can also do this:You can also do this: You can also do this:You can also do this:You can also do this: You can also do this:You can also do this:You can also do this: You can also do this:You can also do this:You can also do this: You can also do this:You can also do this:You can also do this: You can also do this:You can also do this:You can also do this: You can also do this:You can also do this:You can also do this: You can also do this:You can also do this:

```{r stargazer2, echo=FALSE,results='asis'}
cm <- c('DemocracyIndex'='Democracy Index','IndexofEconomicFreedom'    = 'Economic Freedom','(Intercept)' = 'Constant')

modelsummary(models, title = "Models for Military Expenditure",
             stars = TRUE,
             output = "kableExtra",coef_map = cm)

```

I hope you like what you see in the Table \@ref(tab:regs1) and in Table \@ref(tab:regs2). 

# Bibliography

